Embracing the Laws of Physics: \\ Reversible Models of Computation

### 2017-11-24 survey/survey.tex
add 2 citations. start work in survey.tex, from outline.tex

To fully appreciate the missing principle of conventional computing,
one must go back to an old thought experiment by J. C. Maxwell,
codified in a letter that Maxwell wrote to P. G Tait in 1867 -- this
is the letter whose ideas are now well known as the `Maxwell's
Demon'. Maxwell's Demon was a thought experiment that seemed to
indicate that intelligent beings can somehow violate the second law of
thermodynamics, thereby violating physics itself.

Many resolutions were offered for this conundrum (for a compilation,
see Maxwell's Demon by Leff and Rex), but none withstood careful
scrutiny until the establishment of the so called `Landauer's
Principle' in 1961 -- a principle whose experimental validation
happened recently in 2012 by Eric Lutz and others.

>>>>

To fully appreciate one of the principles is missing in conventional computing,
one must go back to an old thought experiment by J. C. Maxwell. This is
codified in a letter that Maxwell wrote to P. G Tait in 1867 -- 
the letter whose ideas are now known as `Maxwell's
Demon'. Maxwell's Demon is a thought experiment that seems to
indicate that intelligent beings can somehow violate the second law of
thermodynamics, thereby violating physics itself.

Many resolutions were offered for this conundrum (for a compilation,
see Maxwell's Demon by Leff and Rex~\cite{leff1990}), but none withstood careful
scrutiny until the establishment of the so called `Landauer's
Principle' in 1961 -- a principle whose experimental validation
happened recently in 2012 by Eric Lutz and others.
